# Week 1, day 2

I planned to examine relationship between water source availabilities and number of reported malaria cases. Therefore, I downloaded data about water sources and malaria cases from WHO. <br>
[water](http://apps.who.int/gho/data/node.main.A1364?lang=en) <br>
[malaria](http://apps.who.int/gho/data/view.main.WSHWATERv?lang=en)
However, the both files about water sources need to be reorganized so they can be merged later.
```{r code=readLines("~/Documents/summerproj/data_science_programming/week_1/day2/water.R")}
```
Here's the result:
Then do the same thing for the `malaria.csv`:
```{r code=readLines("~/Documents/summerproj/data_science_programming/week_1/day2/malaria.R")}
```
finally, merge the result:
```{r code=readLines("~/Documents/summerproj/data_science_programming/week_1/day2/compare.R")}
```

The complete results are too big to be printed here, but the files can be found in the following link:
[water](https://github.com/fhcwcsy/data_science_programming/blob/master/week_1/day2/water_rearranged.csv)
[malaria](https://github.com/fhcwcsy/data_science_programming/blob/master/week_1/day2/malaria_rearranged.csv)
[combined](https://github.com/fhcwcsy/data_science_programming/blob/master/week_1/day2/merged.csv)